Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-08-16 Report/paper.tex
upd
images for the samples submission, scores tables, ..

\paragraph{Train augmentation}: the samples can be horizontally or vertically flipped, rotated (missing pixels are filled with white). CoarseDropout is also used to mask randomly parts of the image. Finally, as the images appeared to be sometimes blury, motion blur is added.

%TODO : Add augmented samples

@@

>>>>

\paragraph{Train augmentation}: the samples can be horizontally or vertically flipped, rotated (missing pixels are filled with white). Coarse dropout, where little square regions are filled in white, is also used to mask randomly parts of the image. Examples of augmented images are shown on figure~\ref{fig:sample_submission_augmented}.

\begin{figure}[htbp]
	\begin{center}
	\includegraphics[width=0.75\columnwidth]{figs/augmented_images.pdf}
	\caption{\label{fig:sample_submission_augmented} Examples of augmented images from the sample submission. The transforms are Horizontal flip, vertical flip, random rotation and coarse dropout. The first column represents the original images and the five following columns examples of augmented images. The little white squares on the images show the coarse dropout.}
	\end{center}
\end{figure}

@@

The cross entropy loss for the training set and the F1 score for the validation split are shown on figure~\ref{fig:sample_submission_losses}. The confusion matrices of the best parameters for the four trained networks are shown on figure~\ref{fig:sample_submission_confusion_matrix}. For every run, the best parameters are the one with the largest validation F1 score.

\begin{figure}[!htbp]
	\caption{\label{fig:sample_submission_losses} The cross entropy loss on the training set and the macro F1 score on the validation fold for the four trained models.}
\end{figure}

\begin{figure}[htbp]
	\begin{center}
		\raisebox{-0.5\height}{\includegraphics[width=0.25\columnwidth]{figs/class_f1_scores_per_team_sample.pdf}}
		\hspace*{.4in}
		\raisebox{-0.5\height}{\includegraphics[width=0.62\columnwidth]{figs/class_f1_scores_per_class_sample.pdf}}
	\end{center}
	\caption{\label{fig:class_team_score_sample} Class F1 scores on the test data per model (left) and per class (right).}
\end{figure}

\begin{figure}[!htbp]
	\begin{tabular}{ccccc}
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_resnet18.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_resnet152.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_efficientnetb3.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_regnety16.png} &
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_average.png}\\
		Resnet18 & Resnet152 & EfficientNet B3 & Regnety 16 & Average model
	\end{tabular}
	\caption{\label{fig:sample_submission_confusion_matrix} Confusion matrices on the validation fold of the best parameters for the four trained models.}
\end{figure}

The macro F1 scores on the public and private test sets of the four trained models are given in table~\ref{table:sample_submission_scores}. We also provide the score for the entry which predicts the class as the one maximizing the average probability of the four models. The class F1 scores for each sample submission per model and per class are displayed on the figure~\ref{fig:class_team_score_sample}.

\begin{table}[htbp]
	\begin{center}
	\begin{tabular}{|c|c|c|}
		\hline
		Model & Public macro F1 & Private macro F1 \\
		\hline
		Resnet18 & 0.79723 & 0.79344 \\
		Resnet152 & 0.80178 & 0.79714 \\
		EfficientNet b3 & 0.80041 & 0.80489\\
		Regnety 16 & 0.80178 & 0.79714 \\
		\hline\hline
		Average model & 0.82687 & 0.82997\\
		\hline
	\end{tabular}
	\end{center}
	\caption{\label{table:sample_submission_scores} Macro F1 scores on the public and private test sets of the challenge.}

\end{table}
